LAGOS lake depth

### 2020-03-26 figures/01_contrasts.Rmd
towards switching between violin and pointrange plots

@@

gg_depth_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%
  group_by(shape_class) %>%
  summarize(lake_maxdepth_m = list(tibble::enframe(
    quantile(lake_maxdepth_m, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = shape_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Depth (m)") + xlab("")
```

```{r gg_area_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_area_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%
  group_by(shape_class) %>%
  summarize(lake_waterarea_ha = list(tibble::enframe(
    quantile(lake_waterarea_ha, probs = c(0.05,0.5,0.95), na.rm = TRUE)))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = shape_class, y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab("Area (ha)") + xlab("")
```

>>>>

```{r define-plots}
contrast_plot <- function(..., plot_type){
  if(plot_type == "violin"){
    violin_plot(...)
  }else{
    pointrange_plot(...)
  }
}

violin_plot <- function(x, grp, varb, label){
  ggplot(data = x) +
  geom_violin(aes(x = UQ(rlang::sym(grp)), y = UQ(rlang::sym(varb))), 
              adjust = 0.8, scale = "count", 
              draw_quantiles = c(0.25, 0.5, 0.75)) +
    ylab(label) + xlab("")
}

quantile_collapse <- function(x){
  list(tibble::enframe(
    quantile(x, probs = c(0.05,0.5,0.95), na.rm = TRUE)))
}

pointrange_plot <- function(x, grp, varb, label){
  x %>%
  group_by(UQ(rlang::sym(grp))) %>%
    dplyr::select(UQ(rlang::sym(grp)), UQ(rlang::sym(varb))) %>%
    summarize_all(quantile_collapse) %>%
    unnest() %>%
  tidyr::spread(name, value) %>%
  ggplot() +
geom_pointrange(aes(x = UQ(rlang::sym(grp)), y = `50%`, 
                      ymin = `5%`, ymax = `95%`)) +
  ylab(label) + xlab("")
}
```

@@

# gg_depth_shape_class <- dt %>%
#   dplyr::filter(shape_class != "neither") %>%  
#   contrast_plot(grp = "shape_class", varb = "lake_maxdepth_m", 
#                 label = "Depth (m)", plot_type = "violin")

gg_depth_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "lake_maxdepth_m", 
                label = "Depth (m)", plot_type = "pointrange")
```

```{r gg_area_shape_class, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
gg_area_shape_class <- dt %>%
  dplyr::filter(shape_class != "neither") %>%  
  contrast_plot(grp = "shape_class", varb = "lake_waterarea_ha", 
                label = "Area (ha)", plot_type = "pointrange")
```
